Risk Perceptions for Wearable Devices

### 2015-03-04 recipient.tex

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
\hline
Rank & Recipient & VUR & Variance & Distribution\\
\hline
1& WORKCONTACTS & 75.16 & 0.879886356298& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_work}\\ 
2& PUBLIC & 72.41 & 0.96322375386& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_pub}\\ 
3& FRIENDS & 69.47 & 1.03749698795 & \includegraphics[width = 2cm, height = 2cm]{tables/recipient_friends}\\ 
4& ALL & 64.78 & 1.1105854312& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_total}\\ 
5& APPSERVER & 42.28 & 1.32348026053& \includegraphics[width = 2cm, height = 2cm]{tables/recipient_app}\\ 
6\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | p{1.5cm} | p{1cm} | p{1cm} | p{2cm} |}
\hline
Rank & Recipient & VUR & Standard Deviation & Distribution\\
\hline
1& WORKCONTACTS & 75.16 & 0.938029850271& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_work}\\ 
2& PUBLIC & 72.41 & 0.981427531711& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_pub}\\ 
3& FRIENDS & 69.47 & 1.01857743937 & \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_friends}\\ 
4& ALL & 64.78 & 1.05385008422& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_total}\\ 
5& APPSERVER & 42.28 & 1.15043470045& \includegraphics[width = 2cm, height = 2cm]{../tables/recipient_app}\\ 
\hline
\end{tabular}
\end{center}
\end{table}
